---
title: "Crawler"
author: "CarlosMercado"
date: "May 20, 2019"
output: html_document
---

# Company Lists 

NASDAQ, NYSE, and AMEX 

```{r}
#install.packages("aws.s3", repos = c("cloudyr" = "http://cloudyr.github.io/drat"))
library(aws.s3)
companylist1 <- "https://www.nasdaq.com/screening/companies-by-name.aspx?letter=0&exchange=nasdaq&render=download"
companylist2 <- "https://www.nasdaq.com/screening/companies-by-name.aspx?letter=0&exchange=nyse&render=download"
companylist3 <-"https://www.nasdaq.com/screening/companies-by-name.aspx?letter=0&exchange=amex&render=download"

download.file(companylist1,destfile = "NASDAQ.csv")
download.file(companylist2, destfile = "NYSE.csv")
download.file(companylist3, destfile = "AMEX.csv")

nasdaq <- read.csv("NASDAQ.csv",stringsAsFactors = FALSE)[,c("Symbol","Name")]
nyse <- read.csv("NYSE.csv",stringsAsFactors = FALSE)[,c("Symbol","Name")]
amex <- read.csv("AMEX.csv",stringsAsFactors = FALSE)[,c("Symbol","Name")]


companies <- rbind.data.frame(nasdaq,nyse,amex,stringsAsFactors = FALSE)

#' write to S3 
#BUCKET <- Sys.getenv("BUCKET_NAME")

write.csv(companies,file = "traded_companies.csv")


```

# Identify Website 

Yahoo Finance + Ticker 

```{r}
library(readxl)
library(stringr)

the_searches_yahoo <- do.call(paste0,
                              args = list("https://finance.yahoo.com/quote/",companies$Symbol))

source("Yahoo_Finance_Crawl/Website_Functions/ticker_to_web.R") 
source("Yahoo_Finance_Crawl/Website_Functions/yahoo_scrape.R") #loops ticker_to_web()
websites <- yahoo_scrape(the_searches_yahoo) # eta: 2hrs on local 

source("Yahoo_Finance_Crawl/Website_Functions/clean_site.R")
source("Yahoo_Finance_Crawl/Website_Functions/site_decisions.R") #loops clean_site()
websites <- site_decisions(websites) 
accepted_sites <- websites[[1]]
exceptions_sites <- websites[[2]]

write.csv(accepted_sites,file = "succeeded_getting_website.csv")
write.csv(exceptions_sites, file = "failed_to_get_website.csv")
```

# Crawl Website for Metadata 

Crawl accepted sites for metadata. 
```{r}
source("Yahoo_Finance_Crawl/Website_Functions/pull_metadata.R")
source("Yahoo_Finance_Crawl/Website_Functions/meta_aggregate.R") # loops pull_metadata() 
# Scrape the sites for metadata 1hr + ----  
 scraped_sites <- meta_aggregate(accepted_sites) 
# may take awhile as well 

write.csv(scraped_sites, file = "metadata_on_accepted_sites.csv")
```

# Match with Wikipedia JSON 

```{r}

library(rjson)

source("Wikipedia_Read/Wiki Functions/wiki_db_creator.R")
source("Wikipedia_Read/Wiki Functions/name_clean.R")
source("Wikipedia_Read/Wiki Functions/match_names.R")
source("Wikipedia_Read/Wiki Functions/multi_match_fix.R")

wiki_df <- wiki_db_creator("Wikipedia_Read/Wikipedia_Data.json")
matched <- match_names(wiki_names = wiki_df$name, 
                       db_names = companies$Name)[,c("wiki_company","companylist_name")]

wiki_complete <- merge(wiki_df,matched,by.x = "name",by.y = "wiki_company")

write(matched, file = "wiki_company_names_crosswalk.csv")
write(wiki_complete, file = "wiki_with_companylist_name_data.csv")
```


# Identifying final datasets 

The original companylist is connected to the website scrape via ticker and name.
The original companylist is connected to the wikipedia data via (companylist) name. Wikipedia name is preserved just in case it is needed for future use. 


